Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-12-11 paper/manuscript.tex
updating figures in text

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig1_what_is_alchemy/Fig1.pdf}    \caption{Illustration of the types of free energies differences that can be calculated using alchemical free energy methods. A: Change in free energy due to a conformational change. B: Partition coefficient such as $\log P$ or $\log D$, here as an example the partition coefficient between methanol and water of a given molecule. C: Free energies of membrane insertions. D: Simulations of protein or other host molecule simulations. E: Absolute free energies of binding of a small molecule to a host (e.g. protein), F: Relative free energy of binding of one molecule with respect to another, here toluene and benzyl alcohol.
    \label{fig:fig1_what_is_alchemy}
    }
\end{figure}

@@

\section{Statistical mechanics can tell us why alchemical free energy calculations work}
\label{sec:theory}
Why would you want to run an alchemical free energy calculation and why do they work? Suppose you want to compute the binding affinity, or free energy of binding, of a ligand $L$ to a protein $P$, given by:
P+L\leftrightharpoons PL
The equilibrium rate of binding is given by the ratio of concentrations of product $[PL]$ and reactants $[P]$, $[L]$:
 K_b^{\circ} = c^{\circ}\frac{[[PL]}{[L][P]}
In order to define a reference state, the standard state is usually defined as $1 \mathrm{mol}/\mathrm{L}$ and $c^\circ$ is the standard state concentration. Thus, the binding free energy is given by:
    \Delta G_{\mathrm{bind}} = -RT\ln K_b^{\circ}
One way to estimate the binding rate is by computing the probability of finding the molecular system in the bound state or the unbound state, making use of partition function ratios, i.e. 
    \includegraphics[width=0.95\linewidth]{paper/figures/fig2_what_is_lam/Fig2.pdf}
    \caption{By introducing a switching function that depends on a factor $\lambda$ it is possible to describe alchemical intermediates. In A it is shown that at $\lambda$ 0 the molecule is a fully interacting phenol and at $\lambda=1$ a fully interacting benzene. Intermediates can be modelled with a softcore potentials whose shape is illustrated in C with dependence on $\lambda$ and D with dependence on the potential energy. B shows an illustration of the probability distribution of the potential energies as the switching function takes values of $\lambda=0$ to $\lambda=1$, intermediates are required for a sufficient overlap in potential energies to estimate a free energy difference between $\lambda=0$ and $\lambda=1$. }
    \label{fig:fig2_what_is_lambda}
    \Delta G_{\mathrm{bind}} = -RT\ln\frac{\int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}{\int_\mathrm{unbound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}
Or more generally in a simplified form the free energy difference between the bound and unbound states is:
\Delta f \equiv f(\mathrm{bound}) - f(\mathrm{unbound}) = -\ln\frac{Z(\mathrm{unbound})}{Z({\mathrm{bound}})},
where $Z = \int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}$ represents the configurational integral. 
How can we compute $\Delta G_{\mathrm{bind}}$ from a molecular dynamics simulation? Running a direct simulation of the binding events is too computationally costly, meaning we cannot easily estimate the configurational integrals of the bound and unbound state from the simulation. This is where alchemical free simulations come in. We can write down a thermodynamic cycle as seen in ~\ref{fig:fig3_binding-thermodynamic-cycle}, for a relative free energy simulation. Based on this cycle we can compute the relative free energy of binding between two compounds $A$ and $B$, by going along the arrow of $\Delta G_{\mathrm{bound}}$, where we introduce a second compound that is similar to the first one. Now $\Delta G_{\mathrm{bound}}$ can be expressed as a ratio of partition functions of toluene (A) and benzyl alcohol (B). 
The defining characteristic of alchemical free energy calculations is the use of a series of alchemically-modified potential functions $U(x; \lambda)$ in which an alchemical parameter $\lambda$ modulates interactions in a manner that cannot occur in real chemical systems.
One or more simulations are used to collect data from a multitude of alchemical states to compute a free energy difference between a chemical state ($\lambda_0$) and another chemical or alchemical reference state ($\lambda_1$),
\begin{eqnarray}
\Delta f &\equiv& f(\lambda_1) - f(\lambda_0) = - \ln \frac{Z(\lambda_1)}{Z(\lambda_0)} , \label{equation:dimensionless-free-energy-difference}
\end{eqnarray}
where the dimensionless free energy $f(\lambda) \equiv \beta F(\lambda)$ is given in terms of partition functions $Z(\lambda)$,
\begin{eqnarray}
Z(\lambda) &=& \int dx \, e^{-u(x; \lambda)} .
\label{equation:partition-function-definition}
\end{eqnarray}
Here, the inverse thermal energy $\beta \equiv (k_B T)^{-1}$ where $k_B$ is the Boltzmann constant and $T$ is the absolute temperature, and the \emph{reduced potential} $u(x; \lambda)$~\cite{shirts2008statistically} is generally given by a trace over thermodynamic parameters with their conjugate dynamical variables,
\begin{eqnarray}
u(x;\lambda) &\equiv& \beta \left[ U(x;\lambda) + p \, V(x) + \sum_{i=1}^N \mu_i \, N_i(x) + \cdots \right] . \label{equation:reduced-potential}
\end{eqnarray}
Here, the collection of thermodynamic and alchemical parameters $\theta \equiv \{\beta, \lambda, p, \mu, \ldots\}$ defines a \emph{thermodynamic state}.
The physical transformation of interest---such as a protein-ligand association process, or transfer free energy among phases---may involve a thermodynamic cycle that requires several free energy differences $\Delta f$ to be computed in order to produce an estimate of the overall desired quantity.

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig3_therm_cyc/Fig3.pdf}
    \caption{{\bf Thermodynamic cycle for computing the relative free energy of binding ($\Delta \Delta G$) between two related small molecules to a supramolecular host.}
    The relative binding free energy difference between two small molecules, $\Delta \Delta G_{\mathrm{bind}, A \rightarrow B} \equiv \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A}$---here benzyl alcohol (top) to toluene (bottom)---can be computed as a difference between two alchemical transformations, $\Delta G_\mathrm{bound} - \Delta G_\mathrm{solvated}$, where $\Delta G_\mathrm{bound}$ represents the free energy change of transforming $A \rightarrow B$ in complex and $\Delta G_\mathrm{solvated}$ the free energy change of transforming $A \rightarrow B$ in solvent.}
    \label{fig:fig3_binding-thermodynamic-cycle}
\end{figure}
\todo[inline, color=green!20]{This section needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

\paragraph{Topologies} A critical first step in relative calculations is to select an approach to these calculations, determining whether to use a \emph{dual topology}, \emph{single topology}, or \emph{hybrid topology} approach to relative calculations.
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{paper/figures/fig4_topol/Fig4.pdf}
    \caption{top: single topology bottom: dual topology Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}
    \label{fig:fig4_topology}
\end{figure} 
The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in their substituents; e.g. consider a transformation of benzene (A) to benzyl alcohol (B)~\ref{fig:fig4_topology}.
In this case the common substructure is the benzene ring, though perhaps may be larger depending on how it is defined, as we discuss below.
In single topology calculations, the overall transformation is set up to involve as few additional atoms as possible, so benzene would be typically changed into benzyl alcohol by changing one of the hydrogens into a carbon. To this new carbon you also find non-interacting atoms called ``dummy atoms'' (retaining their bonded interactions but not interacting with the rest of the system), which will become the two hydrogens attached to the new carbon and the OH group. Bond parameters as well as partial charges are adjusted accordingly. 
Thus, in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in fig.~\ref{fig:fig4_topology} (a). 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig4_topology} (b) depicts how such a dual topology works.

@@

\paragraph{Atom mapping}
Once a particular approach to the topology is selected, a crucial next step is to identify the common atoms which will not be perturbed.
Rigorously, this process essentially comprises a maximal common substructure (MCSS) search of the molecules involved to identify the common substructure -- though the parameters of the MCSS search will differ depending on whether single or dual topology calculations are planned.
Specifically, with a single topology approach in mind, atom types are allowed to change, so a permissive MCSS search can be done, whereas with dual topology a more strict search is required.
\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig5_mcs/MCS.pdf}
    \caption{A: restrictive MCSS match B: ring breaking}
    \label{fig:fig5_mcss}
\end{figure}

@@

\paragraph{Perturbation maps}
Based on the input ligand series a perturbation map can be planned. Recent heuristics have shown the more connected the perturbation network the better, however, there is a way to optimise network structure while minimising the number of perturbations that need to be computed minimising the resulting computational cost~\cite{yang2019optimal}. Sometimes the introduction of intermediates that are not part of the original congeneric series are essential to avoid ring breaking, or dealing with perturbations that would otherwise result in large numbers of atoms to be grown or disappearing. Some commercial tools have underlying good heuristic but may fail with complicated input, needing user validation in particular when dealing with chiral compounds.

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig6_thermo_cyc_abs/fig6_therm_abs.pdf}
    \caption{Absolute thermodynamic cycle}
    \label{fig:fig6_absolute-thermodynamic-cycle}
\end{figure}

@@

@@

\ref{fig:fig7_ampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{paper/figures/fig7_sampl_scheme/sampling_schemes.pdf}
    \caption{\textbf{Four sampling strategies available in different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig7_sampling_scheme}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures/fig9_forward_reverse/Forward_Reverse_Fig.pdf}
    \caption{Free energy (in k$_{B}$T) for two different relative binding free energy (RBFE) perturbations. 
    Each plot shows the estimated free energy change using a varying fraction of total simulation time (up to 5 ns total). 
    The top panel shows the three-step protocol for a perturbation involving 5 perturbed atoms, while the bottom panel shows the same protocol for a perturbation involving 10 perturbed atoms. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}
    \label{fig:convergence_forward_reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures/fig10_equib_detection/fig10_equib.pdf}
    \caption{{\bf Automatic partitioning into equilibration and production regions.}
    \emph{Top:} The average (black line) standard deviation (shaded region) of the reduced potential $u^*$ over many independent replicate simulations started from the same initial conditions show a significant initial transient before relaxing to the true average potential energy.
    \emph{Middle:} A cumulative average (red) of the entire simulation data demonstrates a bias in the estimate of the average potential $<u>$ that persists far beyond the initial transient relaxation time, while averaging a production region that omits the initial transient (blue) eliminates this bias.
    \emph{Bottom:} A simple automated approach to determination of the equilibration boundary $t_0$ suggested in~\cite{chodera2016simple} examines the number of effectively uncorrelated samples $N_{\mathrm{eff}_{[t_0,T]}} = (T-t_0) / g_{[t_0,T]}$ within the proposed production region $[t_0,T]$ by computing the statistical inefficiency $g_{[t_0,T]}$ for that simulation interval.
    $N_{\mathrm{eff}_{[t_0,T]}}$ has the general behavior of increasing linearly as $t_0$ moves backwards from $T$ until the initial transient relaxation is encountered, at which point it plunges.
    The optimal equilibration boundary $t_0$ is selected to maximize the number of uncorrelated samples.
    \emph{Figure adapted from~\cite{chodera2016simple}.}
    \todo[inline]{JDC will update this figure with something similar for a real alchemical free energy calculation.}
    }
    \label{fig:automatic-equilibration-detection}
\end{figure}

@@

\todo[inline, color={green!20}]{ASJSM: write and tidy}

@@

\includegraphics[width=0.95\columnwidth]{paper/figures/fig11_overlap/overlap_matrices.pdf}

@@

\todo[inline, color={green!20}]{ASJSM: Please upload the correct figure here and modify the path below}
\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig8_convergence/free_energy_trajectories.pdf}
    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of ~5230 ns for OA-G3 and ~6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.
}
    \label{fig:freeenergytrajectories}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig1_what_is_alchemy/Figure.pdf}    \caption{Illustration of the types of free energies differences that can be calculated using alchemical free energy methods. A: Change in free energy due to a conformational change. B: Partition coefficient such as $\log P$ or $\log D$, here as an example the partition coefficient between methanol and water of a given molecule. C: Free energies of membrane insertions. D: Simulations of protein or other host molecule simulations. E: Absolute free energies of binding of a small molecule to a host (e.g. protein), F: Relative free energy of binding of one molecule with respect to another, here toluene and benzyl alcohol.
    \label{fig:fig1_what_is_alchemy}
    }
\end{figure}

@@

\section{Statistical mechanics can tell us why alchemical free energy calculations work}
\label{sec:theory}
Why would you want to run an alchemical free energy calculation and why do they work? Suppose you want to compute the binding affinity, or free energy of binding, of a ligand $L$ to a protein $P$, given by:
\begin{equation}
P+L\leftrightharpoons PL
\end{equation}
The equilibrium rate of binding is given by the ratio of concentrations of product $[PL]$ and reactants $[P]$, $[L]$:
\begin{equation}
 K_b^{\circ} = c^{\circ}\frac{[[PL]}{[L][P]}
\end{equation}
In order to define a reference state, the standard state is usually defined as $1 \mathrm{mol}/\mathrm{L}$ and $c^\circ$ is the standard state concentration. Thus, the binding free energy is given by:
\begin{equation}
    \Delta G_{\mathrm{bind}} = -RT\ln K_b^{\circ}
\end{equation}
One way to estimate the binding rate is by computing the probability of finding the molecular system in the bound state or the unbound state, making use of partition function ratios, i.e.

\begin{equation}
    \Delta G_{\mathrm{bind}} = -RT\ln\frac{\int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}{\int_\mathrm{unbound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}}
\end{equation}
Or more generally in a simplified form the free energy difference between the bound and unbound states is:
\begin{equation}
\Delta f \equiv f(\mathrm{bound}) - f(\mathrm{unbound}) = -\ln\frac{Z(\mathrm{unbound})}{Z({\mathrm{bound}})},
\end{equation}
where $Z = \int_\mathrm{bound} \exp(-\beta U(\mathbf{x}))d\mathbf{x}$ represents the configurational integral. 
How can we compute $\Delta G_{\mathrm{bind}}$ from a molecular dynamics simulation? Running a direct simulation of the binding events is too computationally costly, meaning we cannot easily estimate the configurational integrals of the bound and unbound state from the simulation. This is where alchemical free simulations come in. We can write down a thermodynamic cycle as seen in ~\ref{fig:fig3_binding-thermodynamic-cycle}, for a relative free energy simulation. Based on this cycle we can compute the relative free energy of binding between two compounds $A$ and $B$, by going along the arrow of $\Delta G_{\mathrm{bound}}$, where we introduce a second compound that is similar to the first one. Now $\Delta G_{\mathrm{bound}}$ can be expressed as a ratio of partition functions of toluene (A) and benzyl alcohol (B). 
The defining characteristic of alchemical free energy calculations is the use of a series of alchemically-modified potential functions $U(x; \lambda)$ in which an alchemical parameter $\lambda$ modulates interactions in a manner that cannot occur in real chemical systems.
One or more simulations are used to collect data from a multitude of alchemical states to compute a free energy difference between a chemical state ($\lambda_0$) and another chemical or alchemical reference state ($\lambda_1$),
\begin{eqnarray}
\Delta f &\equiv& f(\lambda_1) - f(\lambda_0) = - \ln \frac{Z(\lambda_1)}{Z(\lambda_0)} , \label{equation:dimensionless-free-energy-difference}
\end{eqnarray}
where the dimensionless free energy $f(\lambda) \equiv \beta F(\lambda)$ is given in terms of partition functions $Z(\lambda)$,
\begin{eqnarray}
Z(\lambda) &=& \int dx \, e^{-u(x; \lambda)} .
\label{equation:partition-function-definition}
\end{eqnarray}
Here, the inverse thermal energy $\beta \equiv (k_B T)^{-1}$ where $k_B$ is the Boltzmann constant and $T$ is the absolute temperature, and the \emph{reduced potential} $u(x; \lambda)$~\cite{shirts2008statistically} is generally given by a trace over thermodynamic parameters with their conjugate dynamical variables,
\begin{eqnarray}
u(x;\lambda) &\equiv& \beta \left[ U(x;\lambda) + p \, V(x) + \sum_{i=1}^N \mu_i \, N_i(x) + \cdots \right] . \label{equation:reduced-potential}
\end{eqnarray}
Here, the collection of thermodynamic and alchemical parameters $\theta \equiv \{\beta, \lambda, p, \mu, \ldots\}$ defines a \emph{thermodynamic state}.
The physical transformation of interest---such as a protein-ligand association process, or transfer free energy among phases---may involve a thermodynamic cycle that requires several free energy differences $\Delta f$ to be computed in order to produce an estimate of the overall desired quantity.

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig2_therm_cyc/Figure.pdf}
    \caption{{\bf Thermodynamic cycle for computing the relative free energy of binding ($\Delta \Delta G$) between two related small molecules to a supramolecular host.}
    The relative binding free energy difference between two small molecules, $\Delta \Delta G_{\mathrm{bind}, A \rightarrow B} \equiv \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A}$---here benzyl alcohol (top) to toluene (bottom)---can be computed as a difference between two alchemical transformations, $\Delta G_\mathrm{bound} - \Delta G_\mathrm{solvated}$, where $\Delta G_\mathrm{bound}$ represents the free energy change of transforming $A \rightarrow B$ in complex and $\Delta G_\mathrm{solvated}$ the free energy change of transforming $A \rightarrow B$ in solvent.}
    \label{fig:fig_binding-thermodynamic-cycle}
\end{figure}
\todo[inline, color=green!20]{This section needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

\paragraph{Topologies} A critical first step in relative calculations is to select an approach to these calculations, determining whether to use a \emph{dual topology}, \emph{single topology}, or \emph{hybrid topology} approach to relative calculations.
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig3_topol/Figure.pdf}
    \caption{top: single topology bottom: dual topology Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}
    \label{fig:fig_topology}
\end{figure} 
The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in their substituents; e.g. consider a transformation of benzene (A) to benzyl alcohol (B)~\ref{fig:fig4_topology}.
In this case the common substructure is the benzene ring, though perhaps may be larger depending on how it is defined, as we discuss below.
In single topology calculations, the overall transformation is set up to involve as few additional atoms as possible, so benzene would be typically changed into benzyl alcohol by changing one of the hydrogens into a carbon. To this new carbon you also find non-interacting atoms called ``dummy atoms'' (retaining their bonded interactions but not interacting with the rest of the system), which will become the two hydrogens attached to the new carbon and the OH group. Bond parameters as well as partial charges are adjusted accordingly. 
Thus, in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in fig.~\ref{fig:fig4_topology} (a). 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig4_topology} (b) depicts how such a dual topology works.

@@

\paragraph{Atom mapping}
Once a particular approach to the topology is selected, a crucial next step is to identify the common atoms which will not be perturbed.
Rigorously, this process essentially comprises a maximal common substructure (MCSS) search of the molecules involved to identify the common substructure -- though the parameters of the MCSS search will differ depending on whether single or dual topology calculations are planned.
Specifically, with a single topology approach in mind, atom types are allowed to change, so a permissive MCSS search can be done, whereas with dual topology a more strict search is required.
\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig4_mcs/Figure.pdf}
    \caption{A: restrictive MCSS match B: ring breaking}
    \label{fig:fig_mcss}
\end{figure}

@@

\paragraph{Perturbation maps}
Based on the input ligand series a perturbation map can be planned. Recent heuristics have shown the more connected the perturbation network the better, however, there is a way to optimise network structure while minimising the number of perturbations that need to be computed minimising the resulting computational cost~\cite{yang2019optimal}. Sometimes the introduction of intermediates that are not part of the original congeneric series are essential to avoid ring breaking, or dealing with perturbations that would otherwise result in large numbers of atoms to be grown or disappearing. Some commercial tools have underlying good heuristic but may fail with complicated input, needing user validation in particular when dealing with chiral compounds. 
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig6_types_of_networks/Figure.pdf}
    \caption{\textbf{Examples of perturbation networks} A: Star Shaped network B: Network with cycle closures. The diamond indicates the use of a crystal structure binding mode.}
    \label{fig:fig_types_of_networks}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig5_thermo_cyc_abs/Figure.pdf}
    \caption{Absolute thermodynamic cycle}
    \label{fig:fig_absolute-thermodynamic-cycle}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig7_what_is_lam/Figure.pdf}
    \caption{By introducing a switching function that depends on a factor $\lambda$ it is possible to describe alchemical intermediates. In A it is shown that at $\lambda$ 0 the molecule is a fully interacting phenol and at $\lambda=1$ a fully interacting benzene. Intermediates can be modelled with a softcore potentials whose shape is illustrated in C with dependence on $\lambda$ and D with dependence on the potential energy. B shows an illustration of the probability distribution of the potential energies as the switching function takes values of $\lambda=0$ to $\lambda=1$, intermediates are required for a sufficient overlap in potential energies to estimate a free energy difference between $\lambda=0$ and $\lambda=1$. }
    \label{fig:fig_what_is_lambda}
\end{figure}

@@

\ref{fig:fig_sampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig8_sampl_scheme/Figure.pdf}
    \caption{\textbf{Four sampling strategies available in different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig_sampling_scheme}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/fig10_forward_reverse/Figure.pdf}
    \caption{Free energy (in k$_{B}$T) for two different relative binding free energy (RBFE) perturbations. 
    Each plot shows the estimated free energy change using a varying fraction of total simulation time (up to 5 ns total). 
    The top panel shows the three-step protocol for a perturbation involving 5 perturbed atoms, while the bottom panel shows the same protocol for a perturbation involving 10 perturbed atoms. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}
    \label{fig:convergence_forward_reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/fig11_equib_detection/Figure.pdf}
    \caption{{\bf Automatic partitioning into equilibration and production regions.}
    \emph{Top:} The average (black line) standard deviation (shaded region) of the reduced potential $u^*$ over many independent replicate simulations started from the same initial conditions show a significant initial transient before relaxing to the true average potential energy.
    \emph{Middle:} A cumulative average (red) of the entire simulation data demonstrates a bias in the estimate of the average potential $<u>$ that persists far beyond the initial transient relaxation time, while averaging a production region that omits the initial transient (blue) eliminates this bias.
    \emph{Bottom:} A simple automated approach to determination of the equilibration boundary $t_0$ suggested in~\cite{chodera2016simple} examines the number of effectively uncorrelated samples $N_{\mathrm{eff}_{[t_0,T]}} = (T-t_0) / g_{[t_0,T]}$ within the proposed production region $[t_0,T]$ by computing the statistical inefficiency $g_{[t_0,T]}$ for that simulation interval.
    $N_{\mathrm{eff}_{[t_0,T]}}$ has the general behavior of increasing linearly as $t_0$ moves backwards from $T$ until the initial transient relaxation is encountered, at which point it plunges.
    The optimal equilibration boundary $t_0$ is selected to maximize the number of uncorrelated samples.
    \emph{Figure adapted from~\cite{chodera2016simple}.}
    \todo[inline]{JDC will update this figure with something similar for a real alchemical free energy calculation.}
    }
    \label{fig:automatic-equilibration-detection}
\end{figure}

@@

@@

\includegraphics[width=0.95\columnwidth]{figures/fig12_overlap/Figure.pdf}

@@

\todo[inline, color={green!20}]{ASJSM: Please upload the correct figure here and modify the path below}
\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig9_convergence/Figure.pdf}
    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of ~5230 ns for OA-G3 and ~6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.
}
    \label{fig:freeenergytrajectories}
\end{figure}
